Defending Against Web Application Attacks: Approaches, Challenges and Implications \vspace{-1mm}

### 2017-02-01 docs/paper/questioning.tex
no yellow and watermarks. Also fixed a typo

\newcommand{\hlc}[2][yellow]{ {\sethlcolor{#1} \hl{#2}} }

@@

\usepackage{draftwatermark}
\SetWatermarkText{Confidential}
\SetWatermarkScale{0.4}

@@

\IEEEtitleabstractindextext{
\begin{abstract}
Some of the most dangerous web attacks, such as Cross-Site
Scripting and {\sc sql} injection, exploit vulnerabilities
in web applications that may accept and process
data of uncertain origin without proper validation or
filtering, allowing the injection and execution of
dynamic or domain-specific language code.
These attacks have been constantly topping the lists of
various security bulletin providers despite the numerous
countermeasures that have been proposed over the past 15 years.
In this paper, we provide an analysis on
various defense mechanisms against web code injection attacks.
We propose a model that highlights the key weaknesses enabling these attacks,
and that provides a common perspective for studying the available defenses.
We then categorize and analyze a set of \hlc[yellow]{41} previously proposed defenses 
based on their accuracy, performance,
deployment, security, and availability characteristics.
Detection accuracy is of particular importance,
as our findings show that many defense
mechanisms have been tested in a poor manner. In addition, we observe
that some mechanisms can be bypassed by attackers with knowledge
of how the mechanisms work. Finally, we discuss the results
of our analysis, with emphasis on factors that may hinder
the widespread adoption of defenses in practice.
\vspace{-3mm}
\end{abstract}

@@

Then, we {\it categorize} a selection of representative
protection mechanisms. In our selection we include protection
mechanisms that counter web attacks when they take place,
while we do not consider countermeasures that identify
vulnerabilities using static program analysis~\cite{SZ12}
(which takes place during the development or testing
phases). Similarly, dynamic analysis techniques that examine
applications to identify vulnerabilities that may lead to the attacks
that we described earlier are out of scope as well. Note also, that we
\hlc[yellow]{did not} consider mechanisms that
\hlc[yellow]{have not} been presented in research papers.

@@

\hlc[yellow]{A recent attack called {\sc php} Object Injection
({\sc poi})}~\cite{DKH14} \hlc[yellow]{does not directly involve
the injection of code, but still achieves arbitrary code execution
in the context of a {\sc php} application through the
injection of specially crafted objects
(e.g., as part of cookies).
When deserialized
by the application, these objects result in
arbitrary code execution.}
Note that the exploitation model we propose
in the following Section also captures such attacks.

@@

Cross-site scripting
attacks fall into \hlc[yellow]{three} categories,
{\it non-persistent}
(also known as \emph{reflected}) {\sc xss},
{\it persistent} (also known as \emph{stored}) {\sc xss}
\hlc[yellow]{and \textit{Document Object Model} ({\sc dom})
\textit{-based} \textsc{xss}.}
Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and ends up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server, but immediately becomes part of the
content that is sent back to a user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server-side then re-enters the
application's execution flow and becomes part of the content that is
eventually sent to the user as part of a future response.
\hlc[yellow]{{\sc dom}-based {\sc xss} attacks involve
the modification of the {\sc dom} of a webpage.
The {\sc dom} treats an {\sc html} document
as a tree structure where each node is an
object representing a part of the document.
Each object can be accessed and manipulated
programmatically and any visible changes
may then be reflected in the browser.
In a {\sc dom}-based {\sc xss} attack,
the malicious payload
(e.g., hidden in a well-crafted {\sc url}
that is sent to a user via phishing:
\textsc{n-xss} 1.1)
is executed as a result of
the manipulation of the {\sc dom}
environment
(e.g., when another flawed script accesses the
modified {\sc dom} object)
and is not contained in
the {\sc http} response.
That is,
the malicious payload never reaches the server.
Such an attack can be performed
purely client-side across {\sc html} frames.
Hence,
server-side defenses might not be effective
in this case.}

\hlc[yellow]{A Cross Frame Scripting (\textsc{xfs})
attack is a recent threat that combines
a malicious script with
an {\tt iframe} that loads a legitimate page in
an effort to steal data from a user.
Consider an attacker that lures via social engineering
a user to navigate to a web page the attacker controls.
The attacker's page then loads JavaScript
and an {\sc html} {\tt iframe} pointing to a legitimate site.
Once the user enters his or her
credentials into the legitimate site,
the malicious script records all keystrokes.}

@@

Defenders and attackers are often caught in a cat-and-mouse game,
where countermeasures are bypassed by \hlc[yellow]{savvy} attacks, which are caught
by more sophisticated countermeasures, yet again bypassed by \hlc[yellow]{savvier}
attacks, and so on. We use security to refer to the ability of a
detection mechanism to resist circumvention.

@@

    \caption{\hlc[yellow]{Summary of mechanisms developed to counter application

@@

    and settings.}}

@@

    \vspace{-5.2mm}

@@

  &   \hlc[yellow]{{\sc jsf}low}~\cite{HBBS14} & \hlc[yellow]{62} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r}
  & \hlc[yellow]{2$\times$ ({\sc c})} & \hlc[yellow]{{\sc xss}} \\
  &   \hlc[yellow]{{\sc cowl}}~\cite{SYMRHKM14} & \hlc[yellow]{27} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r}
  & \hlc[yellow]{16\% ({\sc c})} & \hlc[yellow]{{\sc xss}} \\
  &   \hlc[yellow]{Bauer et al.}~\cite{BCJPST15} & \hlc[yellow]{5} & \hlc[yellow]{({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}}
  & \hlc[yellow]{average 55\% ({\sc c})} & \hlc[yellow]{{\sc xss}} \\
  &   \hlc[yellow]{{\sc sif}}~\cite{CVMA07} & \hlc[yellow]{146} & \hlc[yellow]{({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}}
  & \hlc[yellow]{26\% ({\sc s})} & \hlc[yellow]{{\sc sql}i, {\sc xss}} \\

@@

  &   \hlc[yellow]{Hails}~\cite{GLSTMMR12} & \hlc[yellow]{78} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r}
  & \hlc[yellow]{28\% ({\sc s},{\sc c})} & \hlc[yellow]{{\sc sql}i, {\sc xss}} \\
  &   \hlc[yellow]{Aeolus}~\cite{CPSPBCCSL12} & \hlc[yellow]{52} & \hlc[yellow]{({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}}
  & \hlc[yellow]{323.5ms per request ({\sc s})} & \hlc[yellow]{{\sc sql}i, {\sc xss}} \\

@@

\vspace{-1.5mm}
A policy enforcement technique developed by Mozilla,
called {\sc csp} (Content Security
Policy)\footnote{\scriptsize\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}~\cite{SSM10}
is currently supported by many browsers to prevent
{\sc xss} and {\sc csrf} attacks. To eliminate such
attacks, web site administrators
can specify which domains the browser should treat
as valid sources of script and which not.
\hlc[yellow]{These policies are communicated via the {\sc http} headers.}
Then, the browser
(Point {\sc ub}) will only execute scripts that exist in
source files from white-listed domains.
Note that,
if an application involves
embedded scripts, developers must utilize
the {\sc csp}'s {\em nonce} concept.
This is an unpredictable,
random value indicated in
the {\tt script-src} directive,
which in turn is applied as a nonce attribute to
{\tt <script>} elements.
As a result, only those elements that have the
correct nonce will execute.
Even if an attacker
is able to inject markup into the page,
the attack will be prevented by the attacker's
inability to guess the nonce value.
However, attackers may still bypass this feature
and invoke a script from a non-whitelisted source.
To do so, their injected code must
be crafted in a way that the nonce is handled
by the browser as an attribute of the payload~\cite{jigsaw}.

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. BrowserShield~\cite{RDWDE07}
acts as a proxy on the server-side (Point {\sc s}t{\sc b}) to
parse the {\sc html} of server responses and identify
scripts. Then, it rewrites them into safe equivalents
and protects the web user from exploits
that are based on reported browser vulnerabilities.
ConScript~\cite{ML10}, CoreScript~\cite{YCIS07},
and the framework by Phung et al.~\cite{PSC09}
extend JavaScript with new primitive functions that
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place at client-side, in the JavaScript engine of the browser (Point {\sc ub}).
In this way, \hlc[yellow]{{\sc xss}} attacks that take advantage
of functions such as {\tt write} and {\tt eval}, which are
used to assemble innocuous-looking parts into harmful
strings,\footnote{\scriptsize The infamous Sammy worm that
infected MySpace in 2005
utilized the {\tt eval} function to assemble a
malicious script.} would fail.

@@

An issue that involves all taint tracking schemes involves
the difficulty of maintaining accurate taints~\cite{GMPS11}
(e.g., implicit flows~\cite{ME07}).
In such cases, certain, tainted inputs can escape the tracking mechanism.
Keeping track of such input \hlc[yellow]{may be} impractical not only because of the
various technical difficulties, but also because it would raise false alarms.

@@

This category includes mechanisms that borrow
characteristics from both etiological and symptomatic approaches.
\hlc[yellow]{Five} of them focus on the detection of {\sc xss}
attacks and one focuses on {\sc dsl} code injection attacks.

@@

\hlc[yellow]{Information Flow Control ({\sc ifc})
mechanisms combine positive taint tracking and
policy enforcement to prevent {\sc xss} attacks on the
client-side (Point {\sc ub}).
Representative implementations such as
{\sc jsf}low}~\cite{HBBS14}\hlc[yellow]{, {\sc cowl}}~\cite{SYMRHKM14}
\hlc[yellow]{and the framework by Bauer et al.}~\cite{BCJPST15}
\hlc[yellow]{allow developers to express information flow
policies extending the type system of JavaScript.
Then,
the policies are enforced by the JavaScript interpreter
through dynamic checks.}
\hlc[yellow]{{\sc ifc} frameworks do not
focus explicitly on JavaScript and they
have a broader scope.
They can be used to build secure applications,
thus preventing different attacks.
Policies can be provided either as compile-time
program annotations,
or as run-time requirements defined by the user.
Such frameworks include {\sc sif}
(Servlet Information Flow)}~\cite{CVMA07}\hlc[yellow]{,
% Ur/Web}~\cite{C10b}\hlc[yellow]{,
Hails}~\cite{GLSTMMR12}
\hlc[yellow]{, and Aeolus}~\cite{CPSPBCCSL12}.

@@

We group our key observations on the \hlc[yellow]{41} publications that
we consider in this work along the
dimensions we identified in Section~\ref{sec:dimensions}.

@@

Table~\ref{tab:comp} indicates that the authors of 3 out of \hlc[yellow]{41 (7.3\%)}
publications provided a complete tuple of {\sc tp}, {\sc tn}, 
{\sc fp}, and {\sc fn}. On the other hand, we
see that \hlc[yellow]{7} out of \hlc[yellow]{41 (17\%)} were not tested at all.
In these cases, all four elements of the tuple
are not available ({\sc na}). An interesting observation is
that in 10 out of the \hlc[yellow]{41 (24.3\%)}
publications, the evaluation focused on only on attack detection,
and there was no test focusing on false positives.
The corresponding tuples contain {\sc tp} and {\sc fn}
results, but {\sc tn} and {\sc fp} results are not available ({\sc
  na}). This stresses the fact that authors may be more interested in
making sure that their mechanisms can detect known attacks rather than
seeing how they respond under normal conditions. In some cases,
where the number of {\sc tp} results are not quantified, authors did
not mention how many or which attacks they performed. Moreover, in some
cases we observe that even if the authors report the existence of
possible false positive and negative results, they have not quantified
them ({\sc nq}).

@@

Regarding the subjects of tests,
we see that \hlc[yellow]{30} out of \hlc[yellow]{41 (73.1\%)}
mechanisms were tested with real-world
applications known to be vulnerable.
The vulnerabilities associated with these applications
are enlisted in the following providers: the Common
Vulnerabilities and Exposures ({\sc cve})
database,\footnote{\scriptsize\url{https://cve.mitre.org/}}
%~\cite{cve},
the Bugtraq\footnote{\scriptsize\url{http://seclists.org/bugtraq/}}
security mailing list,
%~\cite{bugtraq},
the {\sc xss}ed.com
security bulletin provider,\footnote{\scriptsize\url{www.xssed.com}}
%~\cite{xssed},
Microsoft's security
bulletin\footnote{\scriptsize\url{https://technet.microsoft.com/en-us/security/bulletin}}
%~\cite{microsoftBulletin}
and the
ha.ckers.org\footnote{\scriptsize\url{http://ha.ckers.org/}}
security bulletin provider.
%~\cite{hackers}.
Figure~\ref{fig:defect_sources}
presents how many,
and which publications referred
to which source.
In numerous occasions authors performed tests based
on the same applications.
For example, 12 mechanisms were tested on a
vulnerable version of the {\sc phpbb} bulletin board
software.\footnote{\scriptsize\url{https://www.phpbb.com/}}
%~\cite{phpbb}.

@@

  &   \hlc[yellow]{{\sc jsf}low}~\cite{HBBS14} & \hlc[yellow]{\tick} & \hlc[yellow]{\tick} & \hlc[yellow]{{\sc na}} \\
  &   \hlc[yellow]{{\sc cowl}}~\cite{SYMRHKM14} &  \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} \\
  &   \hlc[yellow]{Bauer et al.}~\cite{BCJPST15} &  \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} \\
  &   \hlc[yellow]{{\sc sif}}~\cite{CVMA07} & \hlc[yellow]{{\bf AO}} & \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} \\

@@

  &   \hlc[yellow]{Hails}~\cite{GLSTMMR12} &  \hlc[yellow]{{\bf AO}} & \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\bf AO}} \\
  &   \hlc[yellow]{Aeolus}~\cite{CPSPBCCSL12} &  \hlc[yellow]{\tick} & \hlc[yellow]{\tick} & \hlc[yellow]{{\sc na}} \\

@@

Table~\ref{tab:avail} presents our findings regarding the availability
of each mechanism in terms of source code and corresponding
executables. We also examined the availability of the testbeds
mentioned in each paper. We see that only \hlc[yellow]{8} out of \hlc[yellow]{41 (19.5\%)} of the
publications provided a link to their mechanism and, 2 from these 6
web pages are currently not available.
In \hlc[yellow]{7} cases the authors made either
the source code or their executables available after their paper got
published. In one case ({\sc csp}~\cite{SSM10}), the source was available before the
publication through the Mozilla community.
Regarding the availability of test materials, we see that
only \hlc[yellow]{4} out of \hlc[yellow]{41 (9.7\%)} publications have currently their testbeds
available.

@@

Table~\ref{tab:comp} shows the performance overhead of each mechanism.
In addition, it indicates if the overhead is incurred at the
server ({\sc s}) or at the client-side ({\sc c}). In almost half of
the approaches, \hlc[yellow]{20} out of \hlc[yellow]{41 (48.7\%)}, the overhead is provided as a
percentage, while in other cases, \hlc[yellow]{8} our of \hlc[yellow]{41 (19.5\%)}, the authors
provide the latency (in ms) that their mechanisms add to the
normal execution time of the protected application.
Note that in some
cases, the times of normal executions are not provided
so it is not possible to convert absolute
time measurements to percentage overheads. In 10 cases (\hlc[yellow]{24.3\%}), the
overhead was either not available ({\sc na})
or not quantified ({\sc nq}).
\hlc[yellow]{For \textsc{php} Aspis}~\cite{PMP11}
\hlc[yellow]{and {\sc jsf}low}~\cite{HBBS14}
\hlc[yellow]{the authors indicate that with
their mechanisms the execution time is doubled.}

@@

\hlc[yellow]{
By design,
{\sc ifc} frameworks provide
limited support for securing legacy applications
and they are not always easy to adopt
because developers need to learn new constructs
to use them.
However,
there are attempts to overcome such issues.
For instance,
the authors of
Aeolus}~\cite{CPSPBCCSL12}
\hlc[yellow]{provide a simple security model
that tries to match the way programmers understand
authorization and access control
with the tracking of information flow.}

@@

Given the fact that the final steps of
{\sc dsl} injection and {\sc csrf} attacks take place
at the server-side, all mechanisms that detect
such attacks are placed at some point within the server-side infrastructure.
From the mechanisms that detect {\sc dsl} code injection
attacks, 3 out of \hlc[yellow]{16 (18.7\%)} do so at the level
of the {\sc rdbms} (Point {\sc db}).
The other \hlc[yellow]{13} are based on interposing on {\sc api} calls related to output
vectors (Point {\sc dbal}).

For frameworks that deal with {\sc xss} attacks, we
see that attack prevention may take place either at the server or
the client-side. In the first case, a proxy is typically placed in front of the server
to examine the server's responses before they reach a user's 
browser. In the second case, a modified browser or a library that is
securely downloaded from the server checks the responses for potential
attacks. We find that the tendency so far is to create frameworks that
perform detection on the client-side: in particular,
\hlc[yellow]{18} out of \hlc[yellow]{30}
frameworks (\hlc[yellow]{60\%}) detect {\sc xss} attacks at the
client-side. Note that the majority of the mechanisms that detect
such attacks on the server can also detect {\sc dsl} code
injection (\hlc[yellow]{9 out of 13}).

@@

\hlc[yellow]{A reasonable argument would be that many defenses
(e.g., many mechanisms coming from the etiological category,
or the {\sc ifc} frameworks), do not need to be
validated purely through testing, since they provide systematic
arguments as to why their design is secure against attacks.
In order for this to hold,
however, their implementation should be flawless
and precisely follow its specification, which may not
be the case in practice. Moreover, even mechanisms that detect attacks
based on their root cause, instead of their observed behavior, may still be
circumvented by evasive attacks.}

@@

\vspace{-0.3mm}
\subsection{\hlc[yellow]{Performance Overhead,
Deployment and Security Remarks}}
\vspace{-0.3mm}

>>>>

@@

% \usepackage{draftwatermark}
% \SetWatermarkText{Confidential}
% \SetWatermarkScale{0.4}

@@

\IEEEtitleabstractindextext{
\begin{abstract}
Some of the most dangerous web attacks, such as Cross-Site
Scripting and {\sc sql} injection, exploit vulnerabilities
in web applications that may accept and process
data of uncertain origin without proper validation or
filtering, allowing the injection and execution of
dynamic or domain-specific language code.
These attacks have been constantly topping the lists of
various security bulletin providers despite the numerous
countermeasures that have been proposed over the past 15 years.
In this paper, we provide an analysis on
various defense mechanisms against web code injection attacks.
We propose a model that highlights the key weaknesses enabling these attacks,
and that provides a common perspective for studying the available defenses.
We then categorize and analyze a set of 41 previously proposed defenses 
based on their accuracy, performance,
deployment, security, and availability characteristics.
Detection accuracy is of particular importance,
as our findings show that many defense
mechanisms have been tested in a poor manner. In addition, we observe
that some mechanisms can be bypassed by attackers with knowledge
of how the mechanisms work. Finally, we discuss the results
of our analysis, with emphasis on factors that may hinder
the widespread adoption of defenses in practice.
\vspace{-3mm}
\end{abstract}

@@

Then, we {\it categorize} a selection of representative
protection mechanisms. In our selection we include protection
mechanisms that counter web attacks when they take place,
while we do not consider countermeasures that identify
vulnerabilities using static program analysis~\cite{SZ12}
(which takes place during the development or testing
phases). Similarly, dynamic analysis techniques that examine
applications to identify vulnerabilities that may lead to the attacks
that we described earlier are out of scope as well. Note also, that we
did not consider mechanisms that
have not been presented in research papers.

@@

A recent attack called {\sc php} Object Injection
({\sc poi})~\cite{DKH14} does not directly involve
the injection of code, but still achieves arbitrary code execution
in the context of a {\sc php} application through the
injection of specially crafted objects
(e.g., as part of cookies).
When deserialized
by the application, these objects result in
arbitrary code execution.
Note that the exploitation model we propose
in the following Section also captures such attacks.

@@

Cross-site scripting
attacks fall into three categories,
{\it non-persistent}
(also known as \emph{reflected}) {\sc xss},
{\it persistent} (also known as \emph{stored}) {\sc xss}
and \textit{Document Object Model} ({\sc dom})
\textit{-based} \textsc{xss}.
Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and ends up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server, but immediately becomes part of the
content that is sent back to a user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server-side then re-enters the
application's execution flow and becomes part of the content that is
eventually sent to the user as part of a future response.
{\sc dom}-based {\sc xss} attacks involve
the modification of the {\sc dom} of a webpage.
The {\sc dom} treats an {\sc html} document
as a tree structure where each node is an
object representing a part of the document.
Each object can be accessed and manipulated
programmatically and any visible changes
may then be reflected in the browser.
In a {\sc dom}-based {\sc xss} attack,
the malicious payload
(e.g., hidden in a well-crafted {\sc url}
that is sent to a user via phishing:
\textsc{n-xss} 1.1)
is executed as a result of
the manipulation of the {\sc dom}
environment
(e.g., when another flawed script accesses the
modified {\sc dom} object)
and is not contained in
the {\sc http} response.
That is,
the malicious payload never reaches the server.
Such an attack can be performed
purely client-side across {\sc html} frames.
Hence,
server-side defenses might not be effective
in this case.

A Cross Frame Scripting (\textsc{xfs})
attack is a recent threat that combines
a malicious script with
an {\tt iframe} that loads a legitimate page in
an effort to steal data from a user.
Consider an attacker that lures via social engineering
a user to navigate to a web page the attacker controls.
The attacker's page then loads JavaScript
and an {\sc html} {\tt iframe} pointing to a legitimate site.
Once the user enters his or her
credentials into the legitimate site,
the malicious script records all keystrokes.

@@

Defenders and attackers are often caught in a cat-and-mouse game,
where countermeasures are bypassed by savvy attacks, which are caught
by more sophisticated countermeasures, yet again bypassed by savvier
attacks, and so on. We use security to refer to the ability of a
detection mechanism to resist circumvention.

@@

    \caption{Summary of mechanisms developed to counter application

@@

    and settings.}

@@

    \vspace{-4.8mm}

@@

  &   {\sc jsf}low~\cite{HBBS14} & 62 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r
  &   2$\times$ ({\sc c}) & {\sc xss} \\
  &   {\sc cowl}~\cite{SYMRHKM14} & 27 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r
  &   16\% ({\sc c}) & {\sc xss} \\
  &   Bauer et al.~\cite{BCJPST15} & 5 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}
  &   average 55\% ({\sc c}) & {\sc xss} \\
  &   {\sc sif}~\cite{CVMA07} & 146 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}
  &   26\% ({\sc s}) & {\sc sql}i, {\sc xss} \\

@@

  &   Hails~\cite{GLSTMMR12} & 78 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r
  &   28\% ({\sc s},{\sc c}) & {\sc sql}i, {\sc xss} \\
  &   Aeolus~\cite{CPSPBCCSL12} & 52 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}
  &   323.5ms per request ({\sc s}) & {\sc sql}i, {\sc xss} \\

@@

\vspace{-1.5mm}
A policy enforcement technique developed by Mozilla,
called {\sc csp} (Content Security
Policy)\footnote{\scriptsize\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}~\cite{SSM10}
is currently supported by many browsers to prevent
{\sc xss} and {\sc csrf} attacks. To eliminate such
attacks, web site administrators
can specify which domains the browser should treat
as valid sources of script and which not.
These policies are communicated via the {\sc http} headers.
Then, the browser
(Point {\sc ub}) will only execute scripts that exist in
source files from white-listed domains.
Note that,
if an application involves
embedded scripts, developers must utilize
the {\sc csp}'s {\em nonce} concept.
This is an unpredictable,
random value indicated in
the {\tt script-src} directive,
which in turn is applied as a nonce attribute to
{\tt <script>} elements.
As a result, only those elements that have the
correct nonce will execute.
Even if an attacker
is able to inject markup into the page,
the attack will be prevented by the attacker's
inability to guess the nonce value.
However, attackers may still bypass this feature
and invoke a script from a non-whitelisted source.
To do so, their injected code must
be crafted in a way that the nonce is handled
by the browser as an attribute of the payload~\cite{jigsaw}.

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. BrowserShield~\cite{RDWDE07}
acts as a proxy on the server-side (Point {\sc s}t{\sc b}) to
parse the {\sc html} of server responses and identify
scripts. Then, it rewrites them into safe equivalents
and protects the web user from exploits
that are based on reported browser vulnerabilities.
ConScript~\cite{ML10}, CoreScript~\cite{YCIS07},
and the framework by Phung et al.~\cite{PSC09}
extend JavaScript with new primitive functions that
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place at client-side, in the JavaScript engine of the browser (Point {\sc ub}).
In this way, {\sc xss} attacks that take advantage
of functions such as {\tt write} and {\tt eval}, which are
used to assemble innocuous-looking parts into harmful
strings,\footnote{\scriptsize The infamous Sammy worm that
infected MySpace in 2005
utilized the {\tt eval} function to assemble a
malicious script.} would fail.

@@

An issue that involves all taint tracking schemes involves
the difficulty of maintaining accurate taints~\cite{GMPS11}
(e.g., implicit flows~\cite{ME07}).
In such cases, certain, tainted inputs can escape the tracking mechanism.
Keeping track of such input may be impractical not only because of the
various technical difficulties, but also because it would raise false alarms.

@@

This category includes mechanisms that borrow
characteristics from both etiological and symptomatic approaches.
Five of them focus on the detection of {\sc xss}
attacks and one focuses on {\sc dsl} code injection attacks.

@@

Information Flow Control ({\sc ifc})
mechanisms combine positive taint tracking and
policy enforcement to prevent {\sc xss} attacks on the
client-side (Point {\sc ub}).
Representative implementations such as
{\sc jsf}low~\cite{HBBS14}, {\sc cowl}~\cite{SYMRHKM14}
and the framework by Bauer et al.~\cite{BCJPST15}
allow developers to express information flow
policies by extending the type system of JavaScript.
Then,
the policies are enforced by the JavaScript interpreter
through dynamic checks.
{\sc ifc} frameworks do not
focus explicitly on JavaScript and they
have a broader scope.
They can be used to build secure applications,
thus preventing different attacks.
Policies can be provided either as compile-time
program annotations,
or as run-time requirements defined by the user.
Such frameworks include {\sc sif}
(Servlet Information Flow)~\cite{CVMA07},
% Ur/Web}~\cite{C10b}\hlc[yellow]{,
Hails~\cite{GLSTMMR12},
and Aeolus~\cite{CPSPBCCSL12}.

@@

We group our key observations on the 41 publications that
we consider in this work along the
dimensions we identified in Section~\ref{sec:dimensions}.

@@

Table~\ref{tab:comp} indicates that the authors of 3 out of 41 (7.3\%)
publications provided a complete tuple of {\sc tp}, {\sc tn}, 
{\sc fp}, and {\sc fn}. On the other hand, we
see that 7 out of 41 (17\%) were not tested at all.
In these cases, all four elements of the tuple
are not available ({\sc na}). An interesting observation is
that in 10 out of the 41 (24.3\%)
publications, the evaluation focused on only on attack detection,
and there was no test focusing on false positives.
The corresponding tuples contain {\sc tp} and {\sc fn}
results, but {\sc tn} and {\sc fp} results are not available ({\sc
  na}). This stresses the fact that authors may be more interested in
making sure that their mechanisms can detect known attacks rather than
seeing how they respond under normal conditions. In some cases,
where the number of {\sc tp} results are not quantified, authors did
not mention how many or which attacks they performed. Moreover, in some
cases we observe that even if the authors report the existence of
possible false positive and negative results, they have not quantified
them ({\sc nq}).

@@

Regarding the subjects of tests,
we see that 30 out of 41 (73.1\%)
mechanisms were tested with real-world
applications known to be vulnerable.
The vulnerabilities associated with these applications
are enlisted in the following providers: the Common
Vulnerabilities and Exposures ({\sc cve})
database,\footnote{\scriptsize\url{https://cve.mitre.org/}}
%~\cite{cve},
the Bugtraq\footnote{\scriptsize\url{http://seclists.org/bugtraq/}}
security mailing list,
%~\cite{bugtraq},
the {\sc xss}ed.com
security bulletin provider,\footnote{\scriptsize\url{www.xssed.com}}
%~\cite{xssed},
Microsoft's security
bulletin\footnote{\scriptsize\url{https://technet.microsoft.com/en-us/security/bulletin}}
%~\cite{microsoftBulletin}
and the
ha.ckers.org\footnote{\scriptsize\url{http://ha.ckers.org/}}
security bulletin provider.
%~\cite{hackers}.
Figure~\ref{fig:defect_sources}
presents how many,
and which publications referred
to which source.
In numerous occasions authors performed tests based
on the same applications.
For example, 12 mechanisms were tested on a
vulnerable version of the {\sc phpbb} bulletin board
software.\footnote{\scriptsize\url{https://www.phpbb.com/}}
%~\cite{phpbb}.

@@

  &   {\sc jsf}low~\cite{HBBS14} & \tick & \tick & {\sc na} \\
  &   {\sc cowl}~\cite{SYMRHKM14} & {\sc na} & {\sc na} & {\sc na} \\
  &   Bauer et al.~\cite{BCJPST15} & {\sc na} & {\sc na} & {\sc na} \\
  &   {\sc sif}~\cite{CVMA07} & {\bf AO} & {\sc na} & {\sc na} \\

@@

  &   Hails~\cite{GLSTMMR12} &  {\bf AO} & {\sc na} & {\bf AO} \\
  &   Aeolus~\cite{CPSPBCCSL12} &  \tick & \tick & {\sc na} \\

@@

Table~\ref{tab:avail} presents our findings regarding the availability
of each mechanism in terms of source code and corresponding
executables. We also examined the availability of the testbeds
mentioned in each paper. We see that only 8 out of 41 (19.5\%) of the
publications provided a link to their mechanism and, 2 from these 6
web pages are currently not available.
In 7 cases the authors made either
the source code or their executables available after their paper got
published. In one case ({\sc csp}~\cite{SSM10}), the source was available before the
publication through the Mozilla community.
Regarding the availability of test materials, we see that
only 4 out of 41 (9.7\%) publications have currently their testbeds
available.

@@

Table~\ref{tab:comp} shows the performance overhead of each mechanism.
In addition, it indicates if the overhead is incurred at the
server ({\sc s}) or at the client-side ({\sc c}). In almost half of
the approaches, 20 out of 41 (48.7\%), the overhead is provided as a
percentage, while in other cases, 8 our of 41 (19.5\%), the authors
provide the latency (in ms) that their mechanisms add to the
normal execution time of the protected application.
Note that in some
cases, the times of normal executions are not provided
so it is not possible to convert absolute
time measurements to percentage overheads. In 10 cases (24.3\%), the
overhead was either not available ({\sc na})
or not quantified ({\sc nq}).
For \textsc{php} Aspis~\cite{PMP11}
and {\sc jsf}low~\cite{HBBS14}
the authors indicate that with
their mechanisms the execution time is doubled.

@@

By design,
{\sc ifc} frameworks provide
limited support for securing legacy applications
and they are not always easy to adopt
because developers need to learn new constructs
to use them.
However,
there are attempts to overcome such issues.
For instance,
the authors of
Aeolus~\cite{CPSPBCCSL12}
provide a simple security model
that tries to match the way programmers understand
authorization and access control
with the tracking of information flow.

@@

Given the fact that the final steps of
{\sc dsl} injection and {\sc csrf} attacks take place
at the server-side, all mechanisms that detect
such attacks are placed at some point within the server-side infrastructure.
From the mechanisms that detect {\sc dsl} code injection
attacks, 3 out of 16 (18.7\%) do so at the level
of the {\sc rdbms} (Point {\sc db}).
The other 13 are based on interposing on {\sc api} calls related to output
vectors (Point {\sc dbal}).

For frameworks that deal with {\sc xss} attacks, we
see that attack prevention may take place either at the server or
the client-side. In the first case, a proxy is typically placed in front of the server
to examine the server's responses before they reach a user's 
browser. In the second case, a modified browser or a library that is
securely downloaded from the server checks the responses for potential
attacks. We find that the tendency so far is to create frameworks that
perform detection on the client-side: in particular,
18 out of 30
frameworks (60\%) detect {\sc xss} attacks at the
client-side. Note that the majority of the mechanisms that detect
such attacks on the server can also detect {\sc dsl} code
injection (9 out of 13).

@@

A reasonable argument would be that many defenses
(e.g., many mechanisms coming from the etiological category,
or the {\sc ifc} frameworks), do not need to be
validated purely through testing, since they provide systematic
arguments as to why their design is secure against attacks.
In order for this to hold,
however, their implementation should be flawless
and precisely follow its specification, which may not
be the case in practice. Moreover, even mechanisms that detect attacks
based on their root cause, instead of their observed behavior, may still be
circumvented by evasive attacks.

@@

\vspace{-0.3mm}
\subsection{Performance Overhead,
Deployment and Security Remarks}
\vspace{-0.3mm}
